---
title: "Museum Parc Financial Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(flexdashboard)
library(assertive)
library(dplyr)
library(ggplot2)
library(knitr)
library(lubridate)
library(readxl)
library(stringr)
library(zoo)
load("../intermediate/cleaned.RData")
source("functions_figures.R")
source("figures.R")
```


Operating expenses
===================================== 

Column {.sidebar}
-----------------------------------------------------------------------

Choose a category and account for further investigation

```{r}
CATEGORY <- "Repair & Maintenance"
ACCOUNT <- "Lighting & Light Bulb Replacement R&M"
```


Column
-----------------------------------------------------------------------

### Year-to-date spending by category

```{r, fig.width = 6, height = 4}
fig_cat_ytd
```

> Bars are shaded based on ratio of YTD spending to YTD budget. + indicates 2016 spending over the same period.


### Year-to-date spending by account

```{r}
  PlotAccountsYTD(CATEGORY)
```

> Bars are shaded based on ratio of YTD spending to YTD budget. + indicates 2016 spending over the same period.


Column
-----------------------------------------------------------------------
### Category spending by month

```{r}
  PlotCategoryByMonth(CATEGORY)
```

> Red line indicates monthly budget. + indicates 2016 spending over the same period.

### Account spending by month

```{r}
PlotAccountByMonth(ACCOUNT)
```

> Red line indicates monthly budget. + indicates 2016 spending over the same period.

Column
-----------------------------------------------------------------------

### Accounts more than 20% over budget YTD

```{r}
accounts_ytd %>% filter(spend_ratio > 1.1 & budget_2017_ytd > 500) %>%
  arrange(desc(spend_2017_ytd - budget_2017_ytd)) %>% ungroup() %>%
  select(category, account_name, budget_2017_ytd, spend_2017_ytd, spend_2016_ytd) %>%
  kable(col.names = c("Category", "Account", "Budget YTD", "Spend YTD", "2016 TD"),
        digits = 0, align = "r", format.args = list(big.mark = ","))
```

> Limited to accounts with more than $500 spent YTD. Sorted in decreasing order of amount over budget.

Payees
=====================================

